msb106_assignment

### 2024-01-17 msb106_assignment.qmd
Endret småting

>>>>

```{r}
data <- read_csv("ilc_lvho01__custom_9371289_linear.csv", 
    locale = locale(date_names = "nb", encoding = "ISO-8859-1"))
View(ilc_lvho01_custom_9371289_linear)
```

```{r}
columns_to_remove <- c("DATAFLOW", "LAST UPDATE", "freq", "incgrp", "building", "unit", "OBS_FLAG")
data <- data[, !(names(data) %in% columns_to_remove)]
```

```{r}
data <- data %>% 
  mutate(deg_urb = case_when(
    deg_urb == "DEG1" ~ "Cities",
    deg_urb == "DEG2" ~ "Towns/Suburbs",
    deg_urb == "DEG3" ~ "Rural areas",
    TRUE ~ deg_urb  # Hvis ingen av de over er oppfylt, behold eksisterende verdi
  ))
```
